---
title: "Save chunk output to file"
author: "Joshua Johnson, Ph.D."
date: "11/23/2017"
output: html_document
---

[StackOverflow](https://stackoverflow.com/questions/33418505/save-knitr-chunk-to-r-file) describes a hooks approach to write a chunk to a file, where the first chunk sets up the function **write_chunk**:

```{r setup, echo=TRUE}
library(knitr)
knit_hooks$set(write_chunk = function(before, options, envir) {
    if (before) {
      fileConn<-file(paste0("chunk_",options$label,".cbs") )# ,open="a")
      writeLines(options$code, fileConn)
      close(fileConn)
    }
})
```

Knitting this document saves the following chunk to file numbers_output.R:

```{r, numbers_output, write_chunk=TRUE}
numbers<-c(1:55)
numbers
```

Next step is to append to chunkbase text file:

from , adding  

> ,open="a"

after file extension as follows:

> .cbs") ,open="a" )

This is a plausible start towards exporting code chunks to the desired chunkbase file. Here's the next chunk to append to the first:

```{r letters_output, write_chunk=TRUE}
#myname<-c("j","o","s","h","u","a")
myname<-c("j","o","s","h")
myname
```



